Usage metrics

### 2020-12-16 analysis/usage.Rmd

r("static eval", static_eval)
r("static evalq", static_evalq)
r("static eval.parent", static_eval.parent)
r("static local", static_local)

r("triggered eval", trig_eval)
r("triggered evalq", trig_evalq)
r("triggered eval.parent", trig_eval.parent)
r("triggered local", trig_local)

r("eval percent call site", ratio(trig_eval, static_eval))
r("evalq percent call site", ratio(trig_evalq, static_evalq))
r("eval.parent percent call site", ratio(trig_eval.parent, static_eval.parent))
r("local percent call site", ratio(trig_local, static_local))
```

>>>>

r("static eval", static_eval)
r("static evalq", static_evalq)
r("static eval parent", static_eval.parent)
r("static local", static_local)

r("triggered eval", trig_eval)
r("triggered evalq", trig_evalq)
r("triggered eval parent", trig_eval.parent)
r("triggered local", trig_local)

r("eval percent call site", ratio(trig_eval, static_eval))
r("evalq percent call site", ratio(trig_evalq, static_evalq))
r("eval parent percent call site", ratio(trig_eval.parent, static_eval.parent))
r("local percent call site", ratio(trig_local, static_local))
```
